---
title: "immigration trussel"
editor_options: 
  chunk_output_type: inline
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage{booktabs} 
    - \usepackage{tabularx}
    - \usepackage{tidy}
output:   
  bookdown::pdf_document2:
  fig_caption: true
  fontsize: 10.5pt
---
henter pakker
```{r hente-pakker, message=FALSE, include=FALSE, echo=FALSE}
library(dplyr) # Kan rense det nye data
library(tidyr)
library(stringr) # Til arbejde med string-data
library(ggplot2) # Til visualisering af resultater
library(viridis)
library(lubridate)
library(ggpubr) # Flere plots sammen
library(openxlsx) # Kan loade og gemme excel
library(ggpubr)
library(tidyverse)
library(haven) # til at åbne datasæt 
library(corrr)
library(psych)
library(Hmisc)
library(xtable)
Sys.setenv("LANGUAGE"="EN")
```

#åbne data
```{r åbne-data, include=FALSE, echo=FALSE}
MPD2020 <- read.csv("../data/MPD2020 mean states.csv")
```


immigrations relevant variabler
per601, per602: positiv og negative way of life
per607, per608: mulitculture, positiv og negativ
per705: underprivilligede minoritet grupper
per601_2: immigration negativ - nye immigranter
per602_2: immigration positivt - nye immigranter
per607_2:multiculture: immigrant diversitet positiv - er i landet
per608_2:multiculture: immigrant assimilation - er i landet
```{r}
immigration <- subset(MPD2020, select = c(id, countryname, edate, per601, per602, per607, per608, per705, per601_2, per602_2, per607_2, per608_2))
```

sum af negativ og positiv omtale multiculture immigrant
```{r}
immigration$per6078_2sum <- immigration$per607_2 + immigration$per608_2
immigration$per6078_sum <- immigration$per607 + immigration$per608
immigration$per6012_sum <- immigration$per601 + immigration$per602
immigration$per6012_2sum <- immigration$per601_2 + immigration$per602_2

```


```{r}
immigration.cor <- correlate(subset(immigration, select = c(per6078_sum, per6012_sum)))
immigration_2.cor <- correlate(subset(immigration, select = c(per6078_2sum, per6012_2sum)))
```

forandring i relevance
```{r}
immigration_c <- subset(MPD2020, select = c(id, countryname, per601_c, per602_c, per607_c, per608_c, per705_c, per601_2_c, per602_2_c, per607_2_c, per608_2_c))
```

sum af negativ og positiv omtale multiculture immigrant
```{r}
immigration_c$per6078_2_csum <- immigration_c$per607_2_c + immigration_c$per608_2_c
immigration_c$per6078_csum <- immigration_c$per607_c + immigration_c$per608_c
immigration_c$per6012_csum <- immigration_c$per601_c + immigration_c$per602_c
immigration_c$per6012_2_csum <- immigration_c$per601_2_c + immigration_c$per602_2_c

```


```{r}
immigration_c.cor <- correlate(subset(immigration_c, select = c(per6078_csum, per6012_csum)))
immigration_c_2.cor <- correlate(subset(immigration_c, select = c(per6078_2_csum, per6012_2_csum)))
```

```{r}
immigration <- full_join(immigration, immigration_c)
```

```{r}
immigration <- immigration %>%
  rowwise()%>%
  mutate(immigration_salience = sum(per6078_2sum + per6012_2sum), ændringer_immigration_salience = sum(per6078_2_csum + per6012_2_csum))

```


```{r}
# x is a matrix containing the data
# method : correlation method. "pearson"" or "spearman"" is supported
# removeTriangle : remove upper or lower triangle
# results :  if "html" or "latex"
  # the results will be displayed in html or latex format
corstars <-function(x, method=c("pearson", "spearman"), removeTriangle=c("upper", "lower"),
                     result=c("none", "html", "latex")){
    #Compute correlation matrix
    require(Hmisc)
    x <- as.matrix(x)
    correlation_matrix<-rcorr(x, type=method[1])
    R <- correlation_matrix$r # Matrix of correlation coeficients
    p <- correlation_matrix$P # Matrix of p-value 
    
    ## Define notions for significance levels; spacing is important.
    mystars <- ifelse(p < .01, "***  ", ifelse(p < .05, "**   ", ifelse(p < .1, "*   ", "    ")))
    
    ## trunctuate the correlation matrix to two decimal
    R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1]
    
    ## build a new matrix that includes the correlations with their apropriate stars
    Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x))
    diag(Rnew) <- paste(diag(R), " ", sep="")
    rownames(Rnew) <- colnames(x)
    colnames(Rnew) <- paste(colnames(x), "", sep="")
    
    ## remove upper triangle of correlation matrix
    if(removeTriangle[1]=="upper"){
      Rnew <- as.matrix(Rnew)
      Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }
    
    ## remove lower triangle of correlation matrix
    else if(removeTriangle[1]=="lower"){
      Rnew <- as.matrix(Rnew)
      Rnew[lower.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }
    
    ## remove last column and return the correlation matrix
    Rnew <- cbind(Rnew[1:length(Rnew)-1])
    if (result[1]=="none") return(Rnew)
    else{
      if(result[1]=="html") print(xtable(Rnew), type="html")
      else print(xtable(Rnew), type="latex") 
    }
}
```

```{r}
corstars(subset(immigration, select = c(per607_2, per608_2, per601_2, per602_2)), result = "latex")
```

```{r}
corstars(subset(immigration, select = c(per607_2_c, per608_2_c, per601_2_c, per602_2_c)), result = "latex")
```


```{r}
rm(immigration_c)
```

